---
output: 
  github_document:
    toc: TRUE

---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = T
)
```


# Part 0. Proposal

Proposing the {ggcircleof5ths} package! 🦄 
<!-- (typical package introduction write up; but actually aspirational) -->

The goal of {ggcircleof5ths} is to make ... easier.


Without the package, we live in the effort-ful world that follows 🏋:

```{r}

major = c("C", "G", "D", "A", "E", "B",
            "Gb","Db", "Ab", "Eb", "Bb", "F")
minor = c("Am", "Em", "Bm", "F#m", "C#m", "G#m", "Ebm",
            "Bbm", "Fm", "Cm", "Gm", "Dm")


get_key_index <-function(key){
  
  if(key %in% major){key_index <- which(major == key)}
  if(key %in% minor){key_index <- which(minor == key)}
  key_index
  
} 

get_key_index(key = "D")


wrap_vector <- function(x, key){
  
  len <- length(x)
  start_index <- get_key_index(key)
  
  c(x[start_index:len], x[1:(start_index-1)])
  
}



spot = 1:12
library(ggstamp)
ggcanvas() +
  stamp_circle(radius = 1.4, x0 = 0, y0 = 0) +
  stamp_text(xy = pos_polygon(x0 = 0, y0 = 0, n = 12,
             radius = 1.1),
             label = wrap_vector(major, "D"),
             size = 6) +
  stamp_circle(radius = .8,x0 = 0, y0 = 0) +
  stamp_text(xy = pos_polygon(n = 12, radius = .5),
             label = wrap_vector(minor, "D"),
             size = 5) +
  stamp_spoke(radius = 1.4, x0 = 0, y0 = 0,
              angle = pi*1:12/6 +
                1/12*pi) + 
  stamp_point(color = "magenta",
              xy = pos_polygon(n = 12,
             radius = 1.1)[which(wrap_vector(major, "D")=="A"),],
             alpha = .2, size = 20)

```


```{r}
library(tidyverse)
compute_panel_circle <- function(data, scales, n = 15){
  
  data |> 
    mutate(group = row_number()) |> 
    crossing(tibble(z = 0:n)) |>
    mutate(around = 2*pi*z/max(z)) |> 
    mutate(x = x0 + cos(around)*r,
           y = y0 + sin(around)*r) 
  
}

geom_circle <- function(...){
  
  ggtemp:::define_layer_temp(
    required_aes = c("x0", "y0", "r"),
    compute_panel = compute_panel_circle,
    geom = ggplot2::GeomPath,
    ...)
  
}

library(ggplot2)
data.frame(x0 = 0:1, y0 = 0:1, r = 1:2/3) |>
  ggplot() +
  aes(x0 = x0, y0 = y0, r = r) +
  geom_circle() +
  aes(fill = r)
```



```{r}
compute_panel_circle5ths <- function(data, scales, n_vertices = 12, rotate = 90){
  
  data |> 
    mutate(group = row_number()) |> 
    crossing(tibble(z = 0:n_vertices)) |>
    mutate(around = 2*pi*z/max(z) + rotate/180*pi) |> 
    mutate(xend = x0, yend = y0) |>
    mutate(x = x0 + cos(around)*r,
           y = y0 + sin(around)*r)
  
}


tibble(x0 = 0, y0 = 0, r = 1) |>
  compute_panel_circle5ths()

compute_group_spokes_labs <- function(data, scales, maj = T, key = "C", rotate = 90-30){
  
  major_ref = c("C", "F" , "Bb", "Eb", "Ab", "Db", "Gb", "B",  "E",  "A",  "D",  "G")
  minor_ref = c("Am", "Dm", "Gm" , "Cm", "Fm", "Bbm", "Ebm", "G#m", "C#m", "F#m", "Bm", "Em") 
    
  if(key %in% major_ref){key_index <- which(major_ref == key)}
  if(key %in% minor_ref){key_index <- which(minor_ref == key)}
  
  keys_reorder_indices <- if(key_index == 1){1:12}else{c(key_index:12, 1:(key_index-1))}
  
  major = major_ref[keys_reorder_indices]
  minor = minor_ref[keys_reorder_indices]
  
  if(maj){label <- major}else{label <- minor}
  
  compute_panel_circle5ths(data = data, scales = scales, 
                           rotate = rotate, n_vertices = 12) |>
    slice(-nrow(data)) |>
    mutate(major = major) |>
    mutate(minor = minor) |>
    mutate(label = label)
  
  
}

tibble(x0 = 0, y0 = 0, r = 1, chord = "c") |>
  compute_group_spokes_labs()


compute_group_chord_highlight <- function(data, scales, maj = T, key = "C", rotate = rotate){
  
  major_ref = c("C", "F" , "Bb", "Eb", "Ab", "Db", "Gb", "B",  "E",  "A",  "D",  "G")

  
  data |>
    mutate(is_minor = !(chord %in% major_ref )) |>
    mutate(r = r / ifelse(is_minor, 2, 1)) |>
  compute_group_spokes_labs(scales = scales, maj = maj, key = key) |>
    filter(major == chord | minor == chord)
  
  
}


tibble(x0 = 0, y0 = 0, r = 1, chord = "F") |>
  compute_group_chord_highlight()

ggtemp:::create_layer_temp("geom_circle",
    required_aes = c("x0", "y0", "r"),
    compute_panel = compute_panel_circle5ths,
    geom = ggplot2::GeomPath)

ggtemp:::create_layer_temp("geom_spoke",
    required_aes = c("x0", "y0", "r"),
    compute_group = compute_group_spokes_labs,
    geom = ggplot2::GeomSegment)

ggtemp:::create_layer_temp("geom_labs",
    required_aes = c("x0", "y0", "r"),
    compute_group = compute_group_spokes_labs,
    geom = ggplot2::GeomText)

ggtemp:::create_layer_temp("geom_chord_highlight",
    required_aes = c("x0", "y0", "r", "chord"),
    compute_group = compute_group_chord_highlight,
    geom = ggplot2::GeomPoint)




library(ggplot2)
library(ggstamp)
ggcanvas() +
  aes(x0 = 0, y0 = 0, r = 1, chord = "C") +
  geom_circle(n_vertices = 50) +
  geom_circle(n_vertices = 50, aes(r = .6)) +
  geom_spoke(rotate = 90/6) +
  geom_labs(maj = T, aes(r = .8)) + 
  geom_labs(maj = F, aes(r = .4)) +
  geom_chord_highlight(aes(r = .8), size = 12, color = "red", alpha = .2)



tibble(phrase = 1:7, chord = LETTERS[1:7]) |>
  ggplot() + 
    aes(x0 = 0, y0 = 0, r = 1, chord = chord) + 
    geom_circle(n_vertices = 50) +
  geom_circle(n_vertices = 50, aes(r = .6)) +
  geom_spoke(rotate = 90/6) +
  geom_labs(maj = T, aes(r = .8)) + 
  geom_labs(maj = F, aes(r = .4), size = 2) +
  geom_chord_highlight(aes(r = .8), size = 12, color = "red", alpha = .2) + 
  coord_equal() +
  facet_wrap(facet = vars(phrase), nrow = 2) +
  labs(title = "An unusual chord progression, A to G in Alphabet")


```




```{r}


geom_chord_cof <- function(r = 1, size = 1, color_highlight = "magenta", alpha_highlight = .4,
                          size_highlight = 7, key = "C"){
  
  list(
  geom_circle(n_vertices = 50, aes(r = r)), 
  geom_circle(n_vertices = 50, aes(r = r*.6)), 
  geom_spoke(rotate = 90/6, aes(r = r)), 
  geom_chord_highlight(aes(r = r*.8), size = size*size_highlight, color = color_highlight, 
                       alpha = alpha_highlight, key = key),
  geom_labs(maj = F, aes(r = r*.4), size = size *2, key = key), 
  geom_labs(maj = T, aes(r = r*.8), key = key) , 
  NULL
  )
  
}


tibble(chord_index = 0:6, 
       chord = LETTERS[1:7]) |>
  ggplot() + 
    aes(x0 = chord_index %% 4 , 
        y0 = -(chord_index %/% 4), 
        chord = chord) + 
    geom_chord_cof(r = .45, key = "D") + 
    coord_equal() +
    labs(title = "An unusual chord progression: A to G in Alphabet")
```

Visualizing some of this discussion... 'A vs Am introduces chromaticism'
https://switchedonpop.com/episodes/olivia-rodrigo-guts-vampire-bad-idea-right

```{r}

tibble::tribble(~ lyric, ~chord, 
"Hate to give the satisfaction, asking how you're doing ... ", "F",
"...now, How's the castle built off people you pretend to care a-...", "A",
"-bout? Just what you wanted, Look at ...", "Bb",
"...you, cool guy, you got it", "Bbm") |>
  ggplot() + 
    aes(x0 = 0, 
        y0 = 0, 
        chord = chord) + 
    geom_chord_cof(r = .45, key = "F") + 
    coord_equal() +
  facet_wrap(~fct_inorder(lyric %>% str_wrap(25)), nrow = 1) +
    labs(title = "Vampire (& Creep) chord progression")
```

  
With the {xxxx} package, we'll live in a different world (🦄 🦄 🦄) where the task is a snap 🫰: 

Proposed API:

```

library(ggcircleof5ths)

df_chords_lyrics |>
 ggplot() + 
 aes(chords = chords) + 
 facet_wrap(vars = fct_inorder(lyrics)) +
 geom_circle5ths(key = "D", r = .5)

```



# Part I. Work out functionality  ✅ 

Here is a function that will do some work...


```{r times_two}
times_two <- function(x){
  
  x*2
  
}
```


## Try it out

```{r}
times_two(4)
```


# Part II. Packaging and documentation  🚧 ✅ 

## Phase 1. Minimal working package

### Bit A. Created package archetecture, running `devtools::create(".")` in interactive session. 🚧 ✅


```{r, eval = F}
devtools::create(".")
```

### Bit B. Added roxygen skeleton? 🚧 ✅

Use a roxygen skeleton for auto documentation and making sure proposed functions are *exported*.  Generally, early on, I don't do much (anything) in terms of filling in the skeleton for documentation, because things may change.

### Bit C. Managed dependencies ? 🚧 ✅

Package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

```{r, eval = F}
usethis::use_package("ggplot2")
```


### Bit D. Moved functions R folder? 🚧 ✅

Use new {readme2pkg} function to do this from readme...

```{r, eval = F}
readme2pkg::chunk_to_r("times_two")
```



### Bit E. Run `devtools::check()` and addressed errors. 🚧 ✅

```{r, eval = F}
devtools::check(pkg = ".")
```

### Bit F. Build package 🚧 ✅

```{r, eval = F}
devtools::build()
```


### Bit G. Write traditional README that uses built package (also serves as a test of build. 🚧 ✅ 

The goal of the {xxxx} package is to ...

Install package with:

```
remotes::installgithub("EvaMaeRey/readme2pkg.template")
```

Once functions are exported you can remove go to two colons, and when things are are really finalized, then go without colons (and rearrange your readme...)

```{r, eval = F}
library(mypacakge)  ##<< change to your package name here
mypacakge:::times_two(10)
```




### Bit H. Chosen a license? 🚧 ✅


```{r, eval = F}
usethis::use_mit_license()
```

### Bit I. Add lifecycle badge (experimental)

```{r, eval = F}
usethis::use_lifecycle_badge("experimental")
```


## Phase 2: Listen & iterate 🚧 ✅

Try to get feedback from experts on API, implementation, default decisions.  Is there already work that solves this problem? 


## Phase 3: Let things settle

### Bit A. Settle on examples.  Put them in the roxygen skeleton and readme. 🚧 ✅

### Bit B. Written formal tests of functions and save to test that folders 🚧 ✅


That would look like this...

```{r test_calc_times_two_works, eval = F}
library(testthat)

test_that("calc times 2 works", {
  expect_equal(times_two(4), 8)
  expect_equal(times_two(5), 10)
  
})
```


```{r, eval = F}
readme2pkg::chunk_to_tests_testthat("test_calc_times_two_works")
```


### Bit C. Added a description and author information in the DESCRIPTION file 🚧 ✅

### Bit D. Addressed *all* notes, warnings and errors. 🚧 ✅

## Phase 4. Promote to wider audience...

### Bit A. Package website built? 🚧 ✅

### Bit B. Package website deployed? 🚧 ✅

## Phase 5: Harden/commit

### Submit to CRAN/RUniverse? 🚧 ✅

# Appendix: Reports, Environment

## Edit Description file

```{r, eval = F}
readLines("DESCRIPTION")
```

## Environment

Here I just want to print the packages and the versions

```{r}
all <- sessionInfo() |> print() |> capture.output()
all[11:17]
```

## `devtools::check()` report

```{r, error = T, results="hide", warning=F}
devtools::check(pkg = ".")
```





